### 2021-12-10 README.Rmd
Update install instructions in README
Test pdf issues on README

The latest version can be installed from [GitHub](https://github.com/xuan-liang/ggmatplot):

```r
# install.packages("remotes")
remotes::install_github("xuan-liang/ggmatplot")
```

@@

The next example, plots out an `errorplot` using the medians and interquartile ranges of each variable.

>>>>

The latest version can be installed from [CRAN](https://CRAN.R-project.org/package=ggmatplot):

```{r eval=FALSE}
install.packages("ggmatplot")
```

Or you can install the development version from [GitHub](https://github.com/xuan-liang/ggmatplot):

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("xuan-liang/ggmatplot")
```

@@

The next example construct out an `errorplot` using the medians and interquartile ranges of each variable.
